### 2013-01-24 patchy-selection-paper.tex
*Empty MediaWiki Message*

Combining this with the calculations above allows us to get a rough sense of the scale of migration between separated patches,
supposing that patches are large enough for local fixation to be stable. If the alleles were not advantageous in the second patch,
the average number of mutant alleles present in a small area $\Delta$
near the second patch, due
to migration from the first patch, would be around $\rho A \exp( -
|\sqrt{s_m} R/\sigma| ) \Delta$. Assuming that the patch is
sufficiently large to give an allele a $2s_B$ probability of becoming established, the rate at which migrants find
themselves in the patch and become established  is approximately
\begin{equation}
\lamda_{Mig,R} = \rho A^2 s_B \exp( -|\sqrt{s_m} R/\sigma| ) \Delta
\end{equation}
. \gc{check my squared here. Do we want to use $q(R)$ here?|
If the establishment rate is low, the time it takes
a mutation to arise that will become established will be  $\sim Exp(\lambda_{mig,R})$

>>>>

Combining this with the calculations above allows us to get a rough sense of the scale of migration between separated patches,
supposing that patches are large enough for local fixation to be stable. If the alleles were not advantageous in the second patch,
the average number of mutant alleles present in a small area $\Delta$
near the second patch, due
to migration from the first patch, would be around $\rho A \exp( -
|\sqrt{s_m} R/\sigma| ) \Delta$. Assuming that the patch is
sufficiently large to give an allele a $2s_B$ probability of becoming established, the rate at which migrants find
themselves in the patch and become established  is approximately
\begin{equation}
\lamda_{Mig,R} = \rho A^2 s_B \exp( -|\sqrt{s_m} R/\sigma| ).
\end{equation}
\gc{check my squared here. Do we want to use $q(R)$ here?|
If this establishment rate is low, the time it takes
a mutation to arise that will become established will be  $\sim Exp(\lambda_{mig,R})$
